Appendix

### 2025-04-09 manuscript_rmarkdown/manuscript_appendix.tex
Main changes to appendix are now complete.

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  a4paper,
]{article}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% definitions for citeproc citations
\NewDocumentCommand\citeproctext{}{}
\NewDocumentCommand\citeproc{mm}{%
  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
\makeatletter
 % allow citations to break across lines
 \let\@cite@ofmt\@firstofone
 % avoid brackets around text for \cite:
 \def\@biblabel#1{}
 \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
\makeatother
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
 {\begin{list}{}{%
  \setlength{\itemindent}{0pt}
  \setlength{\leftmargin}{0pt}
  \setlength{\parsep}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
   \setlength{\leftmargin}{\cslhangindent}
   \setlength{\itemindent}{-1\cslhangindent}
  \fi
  % set entry spacing
  \setlength{\itemsep}{#2\baselineskip}}}
 {\end{list}}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{booktabs}
\usepackage{multirow}
\newtheorem{definition}{Definition}
\DeclareMathOperator*{\argmax}{argmax}
\DeclareMathOperator*{\argmin}{argmin}
\DeclareMathOperator{\sgn}{sgn}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Appendix},
  pdfauthor={Alex Zwanenburg, Steffen Löck},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{Appendix}
\author{Alex Zwanenburg, Steffen Löck}
\date{2025-03-27}

@@

\section{Appendix C: Simulations with other optimisation
criteria}\label{appendix-c-simulations-with-other-optimisation-criteria}

Invariance of location- and scale-invariant power transformations was
assessed using the optimisation criteria in
\href{Appendix\%20B:\%20Optimisation\%20of\%20transformation\%20parameters}{Appendix
B}. This follows the simulation in the main manuscript, where MLE was
used for optimization. In short, we first randomly drew \(10000\) values
from a normal distribution:
\(\mathbf{X}_{\text{normal}} = \left\{x_1, x_2, \ldots, x_{10000} \right\} \sim \mathcal{N}\left(0, 1\right)\),
or equivalently
\(\mathbf{X}_{\text{normal}} = \left\{x_1, x_2, \ldots, x_{10000} \right\} \sim \mathcal{AGN}\left(0, 1/\sqrt{2}, 0.5, 2\right)\).
The second distribution was a right-skewed normal distribution
\(\mathbf{X}_{\text{right}} = \left\{x_1, x_2, \ldots, x_{10000} \right\} \sim \mathcal{AGN}\left(0, 1/\sqrt{2}, 0.2, 2\right)\).
The third distribution was a left-skewed normal distribution
\(\mathbf{X}_{\text{left}} = \left\{x_1, x_2, \ldots, x_{10000} \right\} \sim \mathcal{AGN}\left(0, 1/\sqrt{2}, 0.8, 2\right)\).
We then computed transformation parameter \(\lambda\) using the original
definitions (equations \ref{eqn:box-cox-original} and
\ref{eqn:yeo-johnson-original}) and the location- and scale-invariant
definitions (equations \ref{eqn:box-cox-invariant} and
\ref{eqn:yeo-johnson-invariant}) for each distribution using different
optimisation criteria. To assess location invariance, a positive value
\(d_{\text{shift}}\) was added to each distribution with
\(d_{\text{shift}} \in [1, 10^6]\). Similarly, to assess scale
invariance, each distribution was multiplied by a positive value
\(d_{\text{scale}}\), where \(d_{\text{scale}} \in [1, 10^6]\).

@@

\section{Appendix D: Simulations on clean
data}\label{appendix-d-simulations-on-clean-data}

An alternative to location- and scale-invariant transformations is
normalising feature distributions prior to conventional transformations.
We assessed two normalisation methods were used: 1. z-standardisation,
i.e.~\(x^{\prime}_{i} = \left(x_i - \mu \right) / \sigma\), with \(\mu\)
and \(\sigma\) the mean and standard deviation of feature
\(\mathbf{X}\); and 2. robust scaling,
i.e.~\(x^{\prime}_{i} = \left(x_i - \text{median}\left(\mathbf{X}\right) \right) / \text{IQR}\left(\mathbf{X}\right)\),
with \(\text{IQR}\) representing the interquartile range of feature
\(\mathbf{X}\).

{[}Generated data: clean, n = 30, n = 100, n = 1000, lambda = 0.1, 1.0,
1.9{]}

\begin{table}
\begin{center}
\caption{Residual errors for features from simulated clean data without outliers after Yeo-Johnson transformation to normality.
Several transformation methods include normalisation before transformation, indicated by z-score normalisation (norm.) or robust scaling.}
\label{tab:clean-transformation-residuals-appendix}
\small{
\begin{tabular}{l | l r r r r r r r r r}

none                                  & & 4.0 & 3.4 & 4.6 & 40.1 & 8.9 & 20.8 & 184.6 & 10.1 & 191.8 \\
conventional                          & & 2.7 & 3.3 & 3.6 &  6.5 & 8.1 &  5.6 &  14.2 & 10.1 &  16.1 \\
conventional (z-score norm.)          & & 2.5 & 3.3 & 3.7 &  9.8 & 8.1 &  5.6 &  24.1 & 10.1 &  15.9 \\
conventional (robust scaling)         & & 2.6 & 3.3 & 3.7 &  7.4 & 8.2 &  5.6 &  15.5 & 10.1 &  14.0 \\
Raymaekers-Rousseeuw                  & & 3.8 & 3.3 & 3.6 &  6.5 & 8.5 &  5.6 &  14.4 & 11.0 &  17.6 \\
Raymaekers-Rousseeuw (z-score norm.)  & & 2.6 & 3.3 & 3.7 &  9.8 & 8.5 &  5.6 &  24.1 & 11.1 &  15.9 \\
Raymaekers-Rousseeuw (robust scaling) & & 2.6 & 3.3 & 3.7 &  7.4 & 8.6 &  5.6 &  15.4 & 11.1 &  15.1 \\
invariant                             & & 3.0 & 3.5 & 3.6 &  5.0 & 8.1 &  5.6 &  13.1 & 10.9 &  17.8 \\
robust invariant                      & & 3.0 & 3.3 & 3.6 &  5.2 & 8.3 &  5.9 &  19.9 & 13.6 &  32.9 \\
\bottomrule
\end{tabular}
}
\end{center}
\end{table}

\begin{table}
\begin{center}
\caption{Transformation parameter $\lambda$ for features from simulated clean data without outliers after Yeo-Johnson transformation to normality.
Several transformation methods include normalisation before transformation, indicated by z-score normalisation (norm.) or robust scaling.}
\label{tab:clean-transformation-lambda-appendix}
\small{
\begin{tabular}{l | l r r r r r r r r r}

conventional                          & & 0.6 & 1.2 & 1.5 &  0.0 & 0.9 & 1.6 &  0.1 & 1.0 & 1.9 \\
conventional (z-score norm.)          & & 0.5 & 1.2 & 1.5 & -0.2 & 0.9 & 1.7 & -0.2 & 1.0 & 2.2 \\
conventional (robust scaling)         & & 0.5 & 1.3 & 1.6 & -0.3 & 0.9 & 1.7 & -0.2 & 1.0 & 2.1 \\
Raymaekers-Rousseeuw                  & & 1.0 & 1.2 & 1.5 &  0.0 & 0.7 & 1.6 &  0.1 & 1.0 & 1.9 \\
Raymaekers-Rousseeuw (z-score norm.)  & & 0.7 & 1.2 & 1.5 & -0.2 & 0.7 & 1.7 & -0.2 & 1.0 & 2.2 \\
Raymaekers-Rousseeuw (robust scaling) & & 0.6 & 1.3 & 1.6 & -0.3 & 0.6 & 1.7 & -0.2 & 1.0 & 2.1 \\
invariant                             & & 0.4 & 1.4 & 1.7 &  0.1 & 0.9 & 1.8 &  0.1 & 1.1 & 3.0 \\
robust invariant                      & & 0.4 & 1.3 & 1.5 &  0.0 & 0.8 & 1.7 &  0.0 & 1.1 & 2.0 \\
\bottomrule
\end{tabular}
}
\end{center}
\end{table}

\begin{table}
\begin{center}
\caption{
p-values of empirical central normality tests for features from simulated clean data without outliers after Yeo-Johnson transformation to normality.
Several transformation methods include normalisation before transformation, indicated by z-score normalisation (norm.) or robust scaling.}
\label{tab:clean-transformation-p-value-appendix}
\small{
\begin{tabular}{p{3.5cm} | l r r r r r r r r r}

none                                  & & 0.986 & 0.614 & 0.323 & $<0.001$ & 0.063 & 0.016 & $<0.001$ & 0.997 & $<0.001$ \\
conventional                          & & 0.986 & 0.464 & 0.488 &   0.675  & 0.139 & 0.620 &   0.902  & 0.999 &   0.698 \\
conventional (z-score norm.)          & & 0.979 & 0.440 & 0.477 &   0.200  & 0.141 & 0.770 &   0.419  & 0.999 &   0.723 \\
conventional (robust scaling)         & & 0.982 & 0.439 & 0.484 &   0.487  & 0.130 & 0.683 &   0.883  & 0.999 &   0.817 \\
Raymaekers-Rousseeuw                  & & 0.989 & 0.464 & 0.488 &   0.675  & 0.446 & 0.620 &   0.876  & 0.992 &   0.821 \\
Raymaekers-Rousseeuw (z-score norm.)  & & 0.992 & 0.440 & 0.477 &   0.200  & 0.448 & 0.770 &   0.460  & 0.991 &   0.719 \\
Raymaekers-Rousseeuw (robust scaling) & & 0.993 & 0.439 & 0.484 &   0.487  & 0.422 & 0.683 &   0.887  & 0.991 &   0.848 \\
invariant                             & & 0.993 & 0.355 & 0.461 &   0.720  & 0.153 & 0.490 &   0.910  & 0.999 &   0.682 \\
robust invariant                      & & 0.994 & 0.407 & 0.484 &   0.642  & 0.291 & 0.489 &   0.848  & 0.996 &   0.628 \\
\bottomrule
\end{tabular}
}
\end{center}
\end{table}

\section{Appendix D: Experimental results using location- and
scale-invariant Box-Cox
transformation}\label{appendix-d-experimental-results-using-location--and-scale-invariant-box-cox-transformation}

The effect of using location- and scale-invariant transformations was
investigated using real-world datasets.

\subsection{Invariance}\label{invariance}

Results for Box-Cox transformations of features without outliers are
shown in Figure \ref{fig:experimental-results-invariance-appendix}.

{\centering \includegraphics{manuscript_appendix_files/figure-latex/experimental-results-invariance-appendix-1}

\caption{Quantile-quantile plots for several datasets: age of patients with lung cancer (top row); penguin body mass (middle row); and latitude coordinates of houses sold in Ames, Iowa (bottom row). Multiple quantile-quantile plots are shown: for the original feature (left column); the feature transformed using the conventional Box-Cox transformation and Raymaekers and Rousseeuw's robust adaptation (middle column); and the feature transformed using the non-robust and robust location- and-scale invariant Box-Cox transformations (right column).}\label{fig:experimental-results-invariance-appendix}
\end{figure}

\subsubsection{Age of patients with lung
cancer}\label{age-of-patients-with-lung-cancer}

Applying conventional and invariant Box-Cox transformations to age of
patients with lung cancer (Loprinzi et al. 1994) yielded the following
results: no transformation (sum of residuals with normal distribution
\(\sum r_i = 16.5\), \(p = 0.71\)); conventional transformation
(\(\lambda = 1.9\), \(\sum r_i = 11.5\), \(\mu_{BC} = 1.6 \cdot 10^3\),
\(\sigma_{BC} = 0.4 \cdot 10^3\), \(p = 0.94\)); Raymaekers and
Rousseeuw's robust adaptation (\(\lambda = 1.9\), \(\sum r_i = 11.5\),
\(\mu_{BC} = 1.6 \cdot 10^3\), \(\sigma_{BC} = 0.4 \cdot 10^3\),
\(p = 0.94\)); location- and scale-invariant transformation
(\(\lambda = 1.7\), \(\sum r_i = 11.6\), \(\mu_{BC} = 1.9\),
\(\sigma_{BC} = 0.8\), \(p = 0.94\)); and robust location- and
scale-invariant transformation (\(\lambda = 1.5\), \(\sum r_i = 11.6\),
\(\mu_{BC} = 3.6\), \(\sigma_{BC} = 1.2\), \(p = 0.93\)).

Compared to location- and scale-invariant Yeo-Johnson transformations,
the Box-Cox transformations do not reduce residuals compared to
conventional variants.

\subsubsection{Penguin body mass}\label{penguin-body-mass}

Applying conventional and invariant Box-Cox transformations to the body
mass of penguins (Gorman, Williams, and Fraser 2014) yielded the
following results: no transformation (residual sum \(\sum r_i = 48.0\),
\(p < 0.001\)); conventional transformation (\(\lambda = -0.5\),
\(\sum r_i = 32.2\), \(\mu_{BC} = 2.1\),
\(\sigma_{BC} = 4 \cdot 10^{-3}\), \(p = 0.06\)); Raymaekers and
Rousseeuw's robust adaptation (\(\lambda = -0.5\), \(\sum r_i = 32.2\),
\(\mu_{BC} = 2.1\), \(\sigma_{BC} = 4 \cdot 10^{-3}\), \(p = 0.06\));
location- and scale-invariant transformation (\(\lambda = 0.5\),
\(\sum r_i = 27.3\), \(\mu_{BC} = 0.3\), \(\sigma_{BC} = 0.6\),
\(p = 0.10\)); and robust location- and scale-invariant transformation
(\(\lambda = 0.2\), \(\sum r_i = 25.2\), \(\mu_{BC} = 0.4\),
\(\sigma_{BC} = 0.6\), \(p = 0.44\)).

Just as for location- and scale-invariant Yeo-Johnson transformations,
Box-Cox transformations produced a lower overall residual sum compared
to their conventional counterparts. Similarly, conventional
transformations led to low standard deviation \(\sigma_{YJ}\) of the
body mass feature after transformation.

\subsubsection{Latitude in the Ames housing
dataset}\label{latitude-in-the-ames-housing-dataset}

Applying conventional and invariant Box-Cox transformations to the
latitude of houses in the Ames housing dataset (De Cock 2011) yielded
the following results: no transformation (residual sum
\(\sum r_i = 328\), \(p < 0.001\)); conventional transformation
(\(\lambda = 62.1\), \(\sum r_i = 319\),
\(\mu_{BC} = 1.1 \cdot 10^{99}\), \(\sigma_{BC} = 0.0 \cdot 10^{99}\),
\(p < 0.001\)); Raymaekers and Rousseeuw's robust adaptation
(\(\lambda = 96.0\), \(\sum r_i = 319\),
\(\mu_{BC} = 6.2 \cdot 10^{153}\), \(\sigma_{BC} = 0.3 \cdot 10^{153}\),
\(p < 0.001\)); location- and scale-invariant transformation
(\(\lambda = 1.9\), \(\sum r_i = 312\), \(\mu_{BC} = 2.3\),
\(\sigma_{BC} = 0.9\), \(p < 0.001\)); and robust location- and
scale-invariant transformation (\(\lambda = 1.2\), \(\sum r_i = 316\),
\(\mu_{BC} = 5.5\), \(\sigma_{BC} = 1.4\), \(p < 0.001\)).

Similar to conventional Yeo-Johnson transformations (non-robust and
robust), conventional Box-Cox transformations had high values for the
\(\lambda\) parameter, which could lead to numerical issues. Location-
and scale-invariant Box-Cox transformations did not suffer from this
issue.

\subsection{Robustness against
outliers}\label{robustness-against-outliers}

Results for Box-Cox transformations of features with outliers are shown
in Figure \ref{fig:experimental-results-outlier-robustness-appendix}.

{\centering \includegraphics{manuscript_appendix_files/figure-latex/experimental-results-outlier-robustness-appendix-1}

\caption{Quantile-quantile plots for two datasets with outliers: vehicle fuel consumption (top row), where outliers are related to highly fuel-efficient vehicles; and maximum arterial wall thickness in patients with ischemic stroke (bottom row). Multiple quantile-quantile plots are shown: for the original feature (left column); the feature transformed using the conventional Box-Cox transformation and Raymaekers and Rousseeuw's robust adaptation (middle column); and the feature transformed using the non-robust and robust location- and-scale invariant Box-Cox transformations (right column). Samples with observed quantiles below $-3.0$ or above $3.0$ are indicated by crosses.}\label{fig:experimental-results-outlier-robustness-appendix}
\end{figure}

\subsubsection{Fuel efficiency in the Top Gear
dataset}\label{fuel-efficiency-in-the-top-gear-dataset}

The Top Gear dataset contains data on 297 vehicles, with outliers
related highly fuel-efficient vehicles (Alfons 2021). Applying
conventional and invariant Box-Cox transformations to the fuel
consumption feature yielded the following results: no transformation
(residual sum \(\sum r_i = 54\), \(p=0.58\)); conventional
transformation (\(\lambda = -0.1\), \(\sum r_i = 55\),
\(\mu_{BC} = 3.0\), \(\sigma_{BC} = 0.3\), \(p < 0.001\)); Raymaekers
and Rousseeuw's robust adaptation (\(\lambda = 0.8\), \(\sum r_i = 48\),
\(\mu_{BC} = 29\), \(\sigma_{BC} = 15\), \(p=0.32\)); location- and
scale-invariant transformation (\(\lambda = -0.7\), \(\sum r_i = 44\),
\(\mu_{BC} = 0.6\), \(\sigma_{BC} = 0.2\), \(p < 0.001\)); and robust
location- and scale-invariant transformation (\(\lambda = 1.1\),
\(\sum r_i = 59\), \(\mu_{BC} = 2.4\), \(\sigma_{BC} = 1.8\),
\(p=0.67\)).

\subsubsection{Maximum arterial wall thickness in an ischemic stroke
dataset}\label{maximum-arterial-wall-thickness-in-an-ischemic-stroke-dataset}

The ischemic stroke dataset contains historic data from 126 patients
with risk at ischemic stroke (Kuhn and Johnson 2019). Applying
conventional and invariant Box-Cox transformations to the maximum
arterial wall thickness feature yielded the following results: no
transformation (residual sum \(\sum r_i = 110\), \(p=0.86\));
conventional transformation (\(\lambda = -0.5\), \(\sum r_i = 33\),
\(\mu_{BC} = 1.0\), \(\sigma_{BC} = 0.2\), \(p=0.01\)); Raymaekers and
Rousseeuw's robust adaptation (\(\lambda = 1.1\), \(\sum r_i = 127\),
\(\mu_{BC} = 5.5\), \(\sigma_{BC} = 12\), \(p=0.90\)); location- and
scale-invariant transformation (\(\lambda = -1.0\), \(\sum r_i = 28\),
\(\mu_{BC} = 0.7\), \(\sigma_{BC} = 0.1\), \(p=0.02\)); and robust
location- and scale-invariant transformation (\(\lambda = 0.5\),
\(\sum r_i = 56\), \(\mu_{BC} = 2.2\), \(\sigma_{BC} = 1.4\),
\(p=0.60\)).

\section{Appendix E: Empirical central normality
test}\label{appendix-e-empirical-central-normality-test}

@@

\begin{table}
\begin{center}
\caption{Critical values of test statistic $\tau_{\alpha, n, \kappa = 0.70}$ for
\textbf{central normality} at $\kappa = 0.70$, as a function of significance 
level $\alpha$ and number of instances $n$. The values shown must be divided by $100$.}
\label{tab:central-normality-critical-statistic}
\begin{tabular}{l | r r r r r r r r r}

\toprule
$n$ \textbackslash $\alpha$ & 0.9 & 0.8 & 0.5 & 0.2 & 0.1 & 0.05 & 0.025 & 0.01 & 0.001 \\

\midrule
5     & 10.49 & 13.15 & 17.46 & 22.17 & 25.28 & 27.90 & 29.93 & 31.88 & 34.58 \\
10    &  8.67 & 10.14 & 13.66 & 18.16 & 21.11 & 23.91 & 26.96 & 31.44 & 48.04 \\
20    &  6.77 &  7.71 &  9.97 & 12.96 & 14.93 & 16.70 & 18.24 & 20.33 & 25.24 \\
50    &  4.63 &  5.20 &  6.59 &  8.49 &  9.69 & 10.81 & 11.87 & 13.14 & 16.11 \\
100   &  3.32 &  3.73 &  4.71 &  6.06 &  6.92 &  7.71 &  8.45 &  9.39 & 11.31 \\
200   &  2.37 &  2.66 &  3.35 &  4.29 &  4.89 &  5.46 &  6.00 &  6.67 &  8.02 \\
500   &  1.51 &  1.69 &  2.12 &  2.73 &  3.12 &  3.48 &  3.84 &  4.24 &  5.30 \\
1000  &  1.07 &  1.20 &  1.50 &  1.92 &  2.19 &  2.44 &  2.68 &  3.01 &  3.68 \\
2000  &  0.76 &  0.85 &  1.06 &  1.37 &  1.56 &  1.74 &  1.90 &  2.11 &  2.55 \\
5000  &  0.48 &  0.54 &  0.67 &  0.86 &  0.99 &  1.10 &  1.20 &  1.34 &  1.64 \\
10000 &  0.34 &  0.38 &  0.48 &  0.61 &  0.69 &  0.77 &  0.84 &  0.93 &  1.15 \\
\bottomrule
\end{tabular}
\end{center}
\end{table}

@@

\toprule
$n$ \textbackslash $\alpha$ & 0.9 & 0.8 & 0.5 & 0.2 & 0.1 & 0.05 & 0.025 & 0.01 & 0.001 \\

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  a4paper,
]{article}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% definitions for citeproc citations
\NewDocumentCommand\citeproctext{}{}
\NewDocumentCommand\citeproc{mm}{%
  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
\makeatletter
 % allow citations to break across lines
 \let\@cite@ofmt\@firstofone
 % avoid brackets around text for \cite:
 \def\@biblabel#1{}
 \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
\makeatother
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
 {\begin{list}{}{%
  \setlength{\itemindent}{0pt}
  \setlength{\leftmargin}{0pt}
  \setlength{\parsep}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
   \setlength{\leftmargin}{\cslhangindent}
   \setlength{\itemindent}{-1\cslhangindent}
  \fi
  % set entry spacing
  \setlength{\itemsep}{#2\baselineskip}}}
 {\end{list}}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{placeins}
\newtheorem{definition}{Definition}
\DeclareMathOperator*{\argmax}{argmax}
\DeclareMathOperator*{\argmin}{argmin}
\DeclareMathOperator{\sgn}{sgn}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Appendix},
  pdfauthor={Alex Zwanenburg, Steffen Löck},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{Appendix}
\author{Alex Zwanenburg, Steffen Löck}
\date{2025-04-09}

@@

\subsection{Simulations with other optimisation
criteria}\label{simulations-with-other-optimisation-criteria}

Invariance of location- and scale-invariant power transformations was
assessed using the optimisation criteria in
\href{Appendix\%20B:\%20Optimisation\%20of\%20transformation\%20parameters}{Appendix
B}. This follows the simulation in the main manuscript, where MLE was
used for optimization. In short, we first randomly drew \(10000\) values
from a normal distribution:
\(\mathbf{X}_{\text{normal}} = \left\{x_1, x_2, \ldots, x_{10000} \right\} \sim \mathcal{N}\left(0, 1\right)\),
or equivalently
\(\mathbf{X}_{\text{normal}} = \left\{x_1, x_2, \ldots, x_{10000} \right\} \sim \mathcal{AGN}\left(0, 1/\sqrt{2}, 0.5, 2\right)\).
The second distribution was a right-skewed normal distribution
\(\mathbf{X}_{\text{right}} = \left\{x_1, x_2, \ldots, x_{10000} \right\} \sim \mathcal{AGN}\left(0, 1/\sqrt{2}, 0.2, 2\right)\).
The third distribution was a left-skewed normal distribution
\(\mathbf{X}_{\text{left}} = \left\{x_1, x_2, \ldots, x_{10000} \right\} \sim \mathcal{AGN}\left(0, 1/\sqrt{2}, 0.8, 2\right)\).

We then computed transformation parameter \(\lambda\) using the original
definitions (equations \ref{eqn:box-cox-original} and
\ref{eqn:yeo-johnson-original}) and the location- and scale-invariant
definitions (equations \ref{eqn:box-cox-invariant} and
\ref{eqn:yeo-johnson-invariant}) for each distribution using different
optimisation criteria. To assess location invariance, a positive value
\(d_{\text{shift}}\) was added to each distribution with
\(d_{\text{shift}} \in [1, 10^6]\). Similarly, to assess scale
invariance, each distribution was multiplied by a positive value
\(d_{\text{scale}}\), where \(d_{\text{scale}} \in [1, 10^6]\).

@@

\section{Appendix D: Central normality test and empirical central
normality test critical
values}\label{appendix-d-central-normality-test-and-empirical-central-normality-test-critical-values}

@@

\begin{table}
\begin{center}
\caption{Critical values of test statistic $\tau_{\alpha, n, \kappa = 0.80}$ for
\textbf{central normality} at $\kappa = 0.80$, as a function of significance 
level $\alpha$ and number of instances $n$. The values shown must be divided by $100$.}
\label{tab:central-normality-critical-statistic}
\begin{tabular}{l | r r r r r r r r r}

\toprule
$n$ \textbackslash $\alpha$ & 0.001 & 0.01 & 0.025 & 0.05 & 0.1 & 0.2 & 0.5 & 0.8 & 0.9 \\

\midrule
    5 & 210.79 & 95.75 & 66.27 & 49.69 & 35.93 & 27.60 & 19.29 & 13.41 & 11.00 \\
   10 &  48.04 & 31.44 & 26.96 & 23.91 & 21.11 & 18.16 & 13.66 & 10.14 &  8.67 \\
   20 &  29.13 & 22.13 & 19.75 & 17.94 & 16.00 & 13.81 & 10.54 &  8.18 &  7.18 \\
   50 &  17.31 & 14.01 & 12.63 & 11.48 & 10.28 &  9.00 &  7.00 &  5.54 &  4.94 \\
  100 &  12.19 & 10.04 &  9.02 &  8.21 &  7.38 &  6.47 &  5.04 &  3.99 &  3.56 \\
  200 &   8.68 &  7.11 &  6.40 &  5.83 &  5.22 &  4.57 &  3.59 &  2.86 &  2.56 \\ 
  500 &   5.61 &  4.54 &  4.08 &  3.70 &  3.33 &  2.91 &  2.28 &  1.82 &  1.63 \\
 1000 &   3.93 &  3.19 &  2.87 &  2.60 &  2.33 &  2.05 &  1.61 &  1.29 &  1.15 \\
 2000 &   2.71 &  2.24 &  2.02 &  1.84 &  1.66 &  1.46 &  1.14 &  0.91 &  0.82 \\
 5000 &   1.73 &  1.42 &  1.28 &  1.17 &  1.05 &  0.92 &  0.72 &  0.58 &  0.52 \\
10000 &   1.22 &  1.00 &  0.90 &  0.82 &  0.74 &  0.65 &  0.51 &  0.41 &  0.37 \\
\bottomrule
\end{tabular}
\end{center}
\end{table}

@@

\toprule
$n$ \textbackslash $\alpha$ & 0.001 & 0.01 & 0.025 & 0.05 & 0.1 & 0.2 & 0.5 & 0.8 & 0.9 \\
